### 2019-02-20 sections/intuition.tex
Changed breakfast example

\begin{TASK}
  let makeBreakfast : Task Drink -> Task Food -> Task Unit =
    \makeDrink . \makeFood . makeDrink <&> makeFood >>? \<<d, f>>. eat d f
  let main : Task Unit =
    makeBreakfast (makeTea <?> makeCoffee) makeEgg
\end{TASK}

>>>>

% \begin{TASK}
%   let makeBreakfast : Task Drink -> Task Food -> Task Unit =
%     \makeDrink . \makeFood . makeDrink <&> makeFood >>? \<<d, f>>. eat d f
%   let main : Task Unit =
%     makeBreakfast (makeTea <?> makeCoffee) makeEgg
% \end{TASK}

\begin{TASK}
  let makeBreakfast : Task Drink -> Task Food -> Task <<Drink,Food>> =
    \makeDrink . \makeFood . makeDrink <&> makeFood
  let main : Task Unit =
    (makeBreakfast (makeTea <?> makeCoffee) makeEgg) >>? \<<d, f>>. eat d f
\end{TASK}

% \begin{TASK}
%   let makeBreakfast : Task Drink -> Task Food -> Task Breakfast =
%     \makeDrink . \makeFood . makeDrink <&> makeFood
%   let main : Task Unit =
%     (makeBreakfast (makeTea <?> makeCoffee) makeEgg) >>? \breakfast. eat breakfast
% \end{TASK}
